### 2016-02-14 paper_working_on/paper.tex
paper template initialized

\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Your Paper}

\author{You}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Your abstract.
\end{abstract}

\section{Introduction}

Your introduction goes here! Some examples of commonly used commands and features are listed below, to help you get started. If you have a question, please use the help menu (``?'') on the top bar to search for help or ask us a question.
 So you know me now? I changed this place

\section{Some \LaTeX{} Examples}
\label{sec:examples}

\subsection{How to Leave Comments}

Comments can be added to the margins of the document using the \todo{Here's a comment in the margin!} todo command, as shown in the example on the right. You can also add inline comments:

\todo[inline, color=green!40]{This is an inline comment.}

\subsection{How to Include Figures}

First you have to upload the image file (JPEG, PNG or PDF) from your computer to writeLaTeX using the upload link the project menu. Then use the includegraphics command to include it in your document. Use the figure environment and the caption command to add a number and a caption to your figure. See the code for Figure \ref{fig:frog} in this section for an example. and this place

%\begin{figure}
%\centering
%\includegraphics[width=0.3\textwidth]{frog.jpg}
%\caption{\label{fig:frog}This frog was uploaded to writeLaTeX via the project menu.}
%\end{figure}

\subsection{How to Make Tables}

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. as well as this place

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{How to Write Mathematics}

\LaTeX{} is great at typesetting mathematics. Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
      = \frac{1}{n}\sum_{i}^{n} X_i$$
denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.

\subsection{How to Make Sections and Subsections}

Use section and subsection commands to organize your document. \LaTeX{} handles all the formatting and numbering automatically. Use ref and label commands for cross-references.
will them all in same place
\subsection{How to Make Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}
\dots or with words and descriptions \dots
\begin{description}
\item[Word] Definition
\item[Concept] Explanation
\item[Idea] Text
\end{description}

We hope you find write\LaTeX\ useful, and please let us know if you have any feedback using the help menu above. or not?

\end{document}

### 2016-02-15 paper_working_on/paper.tex
+ framework

@@
 
-\title{Your Paper}
+\title{Biogears in Anesthesia Screen Based Simulation}
 
-\author{You}
+\author{
+  Xiao Han\\
+  \and Liewei Ke
+  \and Guan Wang
+}
 
@@
 \begin{abstract}
-Your abstract.
+Abstract.
 \end{abstract}
 
-\section{Introduction}
+\section{Current physiologic engines and BioGears}
 
-Your introduction goes here!
-Some examples of commonly used commands and features are listed below, to help you get started.
-If you have a question, please use the help menu (``?'') on the top bar to search for help or ask us a question.
- So you know me now? I changed this place
+\section{Show equivalence to current training methods}
+\subsection{Current training methods}
+\subsection{Why using screen based simulation is equivalent to current training methods}
 
-\section{Some \LaTeX{} Examples}
-\label{sec:examples}
+\section{Show physiologically appropriate, responses to key events}
+\subsection{Physical experiments}
+\subsection{Other simulators}
 
-\subsection{How to Leave Comments}
-
-Comments can be added to the margins of the document using the \todo{Here's a comment in the margin!} todo command, as shown in the example on the right. You can also add inline comments:
-
-\todo[inline, color=green!40]{This is an inline comment.}
-
-\subsection{How to Include Figures}
-
-First you have to upload the image file (JPEG, PNG or PDF) from your computer to writeLaTeX using the upload link the project menu.
-Then use the includegraphics command to include it in your document.
-Use the figure environment and the caption command to add a number and a caption to your figure.
-See the code for Figure \ref{fig:frog} in this section for an example.
-and this place
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.3\textwidth]{frog.jpg}
-%\caption{\label{fig:frog}This frog was uploaded to writeLaTeX via the project menu.}
-%\end{figure}
-
-\subsection{How to Make Tables}
-
-Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. as well as this place
-
-\begin{table}
-\centering
-\begin{tabular}{l|r}
-Item & Quantity \\\hline
-Widgets & 42 \\
-Gadgets & 13
-\end{tabular}
-\caption{\label{tab:widgets}An example table.}
-\end{table}
-
-\subsection{How to Write Mathematics}
-
-\LaTeX{} is great at typesetting mathematics.
-Let $X_1, X_2, \ldots, X_n$ be a sequence of independent and identically distributed random variables with $\text{E}[X_i] = \mu$ and $\text{Var}[X_i] = \sigma^2 < \infty$, and let
-$$S_n = \frac{X_1 + X_2 + \cdots + X_n}{n}
-      = \frac{1}{n}\sum_{i}^{n} X_i$$
-denote their mean. Then as $n$ approaches infinity, the random variables $\sqrt{n}(S_n - \mu)$ converge in distribution to a normal $\mathcal{N}(0, \sigma^2)$.
-
-\subsection{How to Make Sections and Subsections}
-
-Use section and subsection commands to organize your document. \LaTeX{} handles all the formatting and numbering automatically. Use ref and label commands for cross-references.
-will them all in same place
-\subsection{How to Make Lists}
-
-You can make lists with automatic numbering \dots
-
-\begin{enumerate}
-\item Like this,
-\item and like this.
-\end{enumerate}
-\dots or bullet points \dots
-\begin{itemize}
-\item Like this,
-\item and like this.
-\end{itemize}
-\dots or with words and descriptions \dots
-\begin{description}
-\item[Word] Definition
-\item[Concept] Explanation
-\item[Idea] Text
-\end{description}
-
-We hope you find write\LaTeX\ useful, and please let us know if you have any feedback using the help menu above. or not?
+\section{Enumerate limits and future work}
+\subsection{Limits of screen based simulation}
+\subsection{Future work}
 

### 2016-02-15 paper_working_on/paper.tex
meeting summary

@@
 \section{Show equivalence to current training methods}
+
+- how to show current training methods
+- do we need to include any human body experiments for comparison
+
 \subsection{Current training methods}
@@
 \section{Show physiologically appropriate, responses to key events}
+
+- bleeding out scenarios, multiple experiments, (mean, root mean squared error, median performance error data recorded)
+- oxygen desaturation (same as aboved)
+
+- patient stop breathing for 30 seconds, 2 mins and recover
+
+- (optional) compare with another dataset asac dataset
+
+- simulate with propofal(200mg), morphine so4(20mg), rocuromium(50mg), succinocloon(100mg), room air(170/70kg)
+
 \subsection{Physical experiments}

### 2016-02-16 paper_working_on/paper.tex
add abstract and intro

@@
   \and Guan Wang
+  \and Mclvor William
 }
@@
 \begin{abstract}
-Abstract.
+The delivery of good medical care concerns patients as well as medical professionals.
+In terms of medical training, mannequins used to be orthodox way to train and demonstrate medical skills for students.
+Nowadays, schools and institutions are adopting more and more high-tech involved methodologies such as Simulation-Based medical education, Virtual Reality in order to provide students with immersive and realistic experience of medical training.
+In Simulation-Based medical education particularly, whether the models of physiology incidents or responses are accurate or not will directly affect the credibility of the simulation.
+In this paper, we will give insights into the physiology simulation and compare the current physiology engine Biogears.
+We will evaluation its function by comparing with simulation provided by CAE Muse system.
+In the end, we will conclude on the performance of Biogears on key points such as authenticity, stability as well as commenting on its limitations.
 \end{abstract}
@@
 \section{Current physiologic engines and BioGears}
+There are a lot of physiologic engines or simulation softwares out there that provides ability to simulate sophisticated body systems.
+Some of them are licensed so medical schools or institutions will have to buy them for usage.
+For example, CAE is a simulation company that provides simulation for aviation, security(defense) and healthcare.
+Their main product for medical simulation is Muse.
+Must provides several simulation scenarios where patients come with different conditions.
+
+Biogears is an open-source physiology engine that provides accurate as well as consistent physiologic simulation of human bodies.
+It contains models that mimic human systems as circuits and substance in physiology for real-time input.
+It can be used as standalone application where physicians could use integrated GUI to simulate customized scenarios or integrated with mannequins, sensors or interfaces that utilize the engine to output consistently.
+
+To thoroughly evaluate Biogears simulation, we repeatedly conducted several experiments on normal patients and calculate key variables within the patients.
+We evaluate engine stability by calculating the mean squared error of several vital signs.
+We evaluate engine authenticity by comparing with CAE simulation result and consulting with real doctors and physicians.
 
@@
 - how to show current training methods
-- do we need to include any human body experiments for comparison
 

### 2016-02-17 paper_working_on/paper.tex
add experiment intro

@@
 
+The reason why physicians don't buy into simulation-based software is due to the fundamental distrust in the models simulation software utilized to generate all the signals and data.
+And yet, there is no uniformly consented algorithms to describe the complicated nature of human bodies.
+Thus, the most reliable way to evaluate whether a simulation is fit for real scenario operations is to compare them with the common sense of physicians and doctors.
+For example, one of the most common thoughts of physicians about the authenticity of scenarios generated by simulation is to see the heart rate of patient when the patient is given different dosage of morphine.
+If you inject a small dosage of morphine it should somehow make the patient calm down and reduce the heart rate but if you inject more morphine than you should, the drug may be likely to kill a patient.
+
+Inspired by the previous work from this paper \cite{measure_repeatability}
+
 - bleeding out scenarios, multiple experiments, (mean, root mean squared error, median performance error data recorded)
@@
 
+\begin{thebibliography}{1}
+
+  \bibitem{measure_repeatability} Cumin, David, Charlotte Chen, and Alan F. Merry. "Measuring the repeatability of simulated physiology in simulators." Simulation in Healthcare 10.6 (2015): 336-344.
+
+  \bibitem{impj}
+
+  \bibitem{norman}
+
+  \bibitem{fo}
+
+  \end{thebibliography}
 \end{document}

### 2016-02-17 paper_working_on/paper.tex
add bleeding out scenario intro

@@
 
-Inspired by the previous work from this paper \cite{measure_repeatability}
+Inspired by the previous work from this paper \cite{measure_repeatability}, we think the quality of a simulation system will also be determined by the stability of experiments under the same or similar circumstances.
+After consulting with physicians from UPMC and Biogears team, we enumerate several representative experiments and ran both Biogears and CAE simulation on them.
+Later we presented the result in graphs and tables for visuality.
+
+\subsection{Bleeding Out Scenarios}
+
+Bleeding patients are often seen in trauma and emergency rooms.
+The cause of this symptom varies.
+Car accident, Blood vessel abnormalities, blood disorders, tumors, to name a few.
+We believe that to see how simulation engine reacts to a patient who is suffering from bleeding would be a good way to see how it models human bodies change as time goes by.
+
+To run this experiment on Biogears, we tested it using built-in GUI of Biogears that provides dozens of substances simulation.
 

### 2016-02-17 paper_working_on/paper.tex
add two graph for bleeding out experiments

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=10cm]{bleeding_out_HeartRate_vs_Time.jpg}
+  \caption{heart rate changes when patient bleeds out in Biogears simulation}
+  \label{fig:patient bleeding}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=10cm]{bleeding_out_RespirationRate_vs_Time.jpg}
+  \caption{heart rate changes when patient bleeds out in Biogears simulation}
+  \label{fig:patient bleeding}
+\end{figure}
+
+In reality, it is not the case that patient could live with continuous hemorrhage: The heart rate of patient will increase because with blood loss there is not enough oxygen so his/her heart has to pump faster and absorb more oxygen.
+His respiratory rate will rise.
+But after a while, when he/she eventually loses
+
 - bleeding out scenarios, multiple experiments, (mean, root mean squared error, median performance error data recorded)

### 2016-02-21 paper_working_on/paper.tex
add the stop breathing experiments

@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage{verbatim}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=10cm]{bleeding_out_HeartRate_vs_Time.jpg}
-  \caption{heart rate changes when patient bleeds out in Biogears simulation}
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{bleeding_out_HeartRate_vs_Time.jpg}}
+     \caption{heart rate changes}
      \label{fig:patient bleeding}
-\end{figure}
 
-\begin{figure}
-  \centering
-  \includegraphics[width=10cm]{bleeding_out_RespirationRate_vs_Time.jpg}
-  \caption{heart rate changes when patient bleeds out in Biogears simulation}
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{bleeding_out_RespirationRate_vs_Time.jpg}}
+     \caption{respiratory rate changes}
      \label{fig:patient bleeding}
+   \end{minipage}
 \end{figure}
@@
 
-\subsection{Physical experiments}
-\subsection{Other simulators}
+\subsection{oxygen desaturation Scenarios}
+
+Oxygen Desaturation is another incident that's often observed by physicians where it occurs during sleep of patients with chronic obstructive lung disease and is often caused by sleep-disordered breathing(SDB)\cite{low_oxygen_sleep}.
+When this happens, the concentration of oxygen in patients' blood decreases and it may result in various symptoms, such as shortness of breath.
+
+For physicians, being able to track how long patient has been experiencing such symptoms is important.
+For example, in surgery, if patient suffered from deficiency of blood oxygen for a long time, it may cause their brains irreversible damage.
+So we also designed experiments to see how Biogears reacts to patients simulation who are suffering from lack of oxygen for different range of time.
+In reality, if a patient experience lack of oxygen in blood for a longer time, it will be harder or even impossible for his brain and body to recover from this disease.
+
+In Biogears, we set up two patients to stop breathing for 30 and 120 seconds and then restore the their air supply. The following graphs are the simulation result for them.
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{30_OxygenSaturation_vs_Time.jpg}}
+     \caption{oxygen saturation changes}
+     \label{fig:patient stoping breathing}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{120_OxygenSaturation_vs_Time.jpg}}
+     \caption{oxygen saturation changes}
+     \label{fig:patient stoping breathing}
+   \end{minipage}
+\end{figure}
+
+As we can see on the graphs, both patients' oxygen saturation drops as they stopped breathing and once we restore the air supply, they recovered from it in 25 seconds.
+And there actually isn't difference in how long it will take them to recover from the deficiency.
+It shows that Biogears is currently not capable to simulate this complex yet delicate recovery scenarios.
+
+%\subsection{Physical experiments}
+%\subsection{Other simulators}
 
@@
 
-  \bibitem{impj}
+  \bibitem{low_oxygen_sleep}Kearley, R., et al.
+"The effect of low flow oxygen on sleep-disordered breathing and oxygen desaturation.
+A study of patients with chronic obstructive lung disease." CHEST Journal 78.5 (1980): 682-685.
 

### 2016-02-22 paper_working_on/paper.tex
extract the data from cae experiment and add jpg to paper

@@
 
-\subsection{oxygen desaturation Scenarios}
+\subsection{Oxygen Desaturation Scenarios}
 
@@
 And there actually isn't difference in how long it will take them to recover from the deficiency.
-It shows that Biogears is currently not capable to simulate this complex yet delicate recovery scenarios.
+It shows that Biogears is currently not capable of simulating this complex yet delicate recovery scenarios.
+
+\subsection{Tests for Common Drugs}
+
+\subsubsection{Succinycholine Simulation}
+
+Succinycholine is a drug that could trigger short-period muscle relaxation and therefore used as an approach to induce short-period paralysis.
+In the discipline of anesthesia, it is used widely for emergency medicine and trauma care due to its fast-acting and short-duration nature.
+Therefore, adjusting its dosage to multiple scenarios is important for those who wish to practice their knowledge and become anaesthetist in the future.
+
+In Biogears, we set up the Succinycholine's dosage to be 5 mg as suggested by Dr. Mchvor. We simulated the scenario for  
+more than 900 seconds cause it takes time for patient to recover from paralysis.
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Succinylcholine_HeartRate_vs_Time.jpg}}
+     \caption{Heart Rate changes}
+     \label{fig:given 5 mg Succinylcholine}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Succinylcholine_OxygenSaturation_vs_Time.jpg}}
+     \caption{Oxygen Saturation changes}
+     \label{fig:given 5 mg Succinylcholine}
+   \end{minipage}
+\end{figure}
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Succinylcholine_ArterialPressure_vs_Time.jpg}}
+     \caption{Blood Pressure changes}
+     \label{fig:given 5 mg Succinylcholine}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Succinylcholine_RespirationRate_vs_Time.jpg}}
+     \caption{Respiration Rate changes}
+     \label{fig:given 5 mg Succinylcholine}
+   \end{minipage}
+\end{figure}
+
+In CAE, we set up the Succinycholine's dosage to be 77mg cause Muse only provides options for injection corresponding to the patient weight. We simulated the scenario for more than
+
+When observing the result graphs, we could see that patient stopped breathing for nearly 4 minutes.
+
+\subsubsection{Rocuronium 50 mg Simulation}
+
+\subsubsection{Propofol 200 mg Simulation}
+
+\subsubsection{Morphine 40 mg Simulation}
+
+\subsubsection{Fentanyl 500 ug Simulation}
 

### 2016-02-22 data-processing-script/plot_csv.py

@@ -1,0 +1,47 @@
+import pandas as pd
+#PatientTime, SCETime, WorldTime, HR, SBP, DBP, RR, SpO2, MAP, CVP, PAS, PAD, PCWP, CO, VT, PAO2, PACO2, PaO2 , PaCO2 , Hb, Hct, pH, TBody, TBlood, ICP, II, PAN2, Alv. ISO., Alv. SEV., Alv. HAL., Alv. ENF., pvO2, pvCO2, C-SPINE X, C-SPINE Y
+# names = ['SCETime', 'WorldTime', 'HR','SBP','DBP','RR','SpO2','MAP','CVP',
+#         'PAS','PAD','PCWP','CO','VT','PAO2','PACO2','PaO2','PaCO2','Hb',
+#         'Hct','pH','TBody','TBlood', 'ICP','II','PAN2','Alv. ISO.','Alv. SEV.'
+#         'Alv. HAL.','Alv. ENF.','pvO2','pvCO2','C-SPINE X', 'C-SPINE Y']
+def recollect_data(csv_file = '2016-02-21_2103_PhysiologicalDataLog.csv'):
+        #read the file from the csv_from_cae folder
+        df = pd.read_csv('csv_from_cae/'+csv_file, header = None)
+        i = 0
+
+        #time_stamp
+        time_stamp = []
+        for row in df[2]:
+                time_stamp.append(row)
+
+        #HR
+        HR = []
+        for row in df[3]:
+                print row
+                HR.append(int(row))
+
+        #SBP
+        SBP = []
+        for row in df[4]:
+                SBP.append(int(row))
+
+        #DBP
+        DBP = []
+        for row in df[5]:
+                DBP.append(int(row))
+
+        #RR
+        RR = []
+        for row in df[6]:
+                RR.append(int(row))
+
+        #SpO2
+        SpO2 = []
+        for row in df[7]:
+                SpO2.append(int(row))
+
+        return time_stamp,HR,SBP,DBP,RR,SpO2
+
+if __name__ == "__main__":
+        #test
+        time_stamp,_,_,_,_,_ = recollect_data()

### 2016-02-23 paper_working_on/paper.tex
add biogears simulation results for Propofol and Rocuronium

@@
 more than 900 seconds cause it takes time for patient to recover from paralysis.
+
+When observing the result graphs, we could see that patient stopped breathing for nearly 4 minutes.
+
 \begin{figure}[!htb]\centering
@@
 
-In CAE, we set up the Succinycholine's dosage to be 77mg cause Muse only provides options for injection corresponding to the patient weight. We simulated the scenario for more than
-
-When observing the result graphs, we could see that patient stopped breathing for nearly 4 minutes.
+In CAE, we set up the Succinycholine's dosage to be 77mg cause Muse only provides options for injection corresponding to the patient weight. We simulated the scenario for 6 minutes.
 
@@
 
+Rocuronium is an anaesthesia drug that blocks neuromuscular signals in muscles and therefore used as muscle relaxant.
+It is widely used for surgery or mechanical ventilation with the nature of rapid onset and intermediate duration.
+For the experiment, we set up both normal patient and patient with asthma history to see how they react to the drug.(Asthma patient will likely suffer from allergy)
+
+In the experiment, we gave each patient 50 mg Rocuronium and record the response of vital signs as following graphs:
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Rocuronium_HeartRate_vs_Time.jpg}}
+     \caption{Heart Rate changes}
+     \label{fig:given 50 mg Rocuronium}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Rocuronium_OxygenSaturation_vs_Time.jpg}}
+     \caption{Oxygen Saturation changes}
+     \label{fig:given 50 mg Rocuronium}
+   \end{minipage}
+\end{figure}
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Rocuronium_ArterialPressure_vs_Time.jpg}}
+     \caption{Blood Pressure changes}
+     \label{fig:given 50 mg Rocuronium}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Rocuronium_RespirationRate_vs_Time.jpg}}
+     \caption{Respiration Rate changes}
+     \label{fig:given 50 mg Rocuronium}
+   \end{minipage}
+\end{figure}
+
 \subsubsection{Propofol 200 mg Simulation}
+
+Before and during the surgery, Propofol is widely used as a way of sedation to decrease level of consciousness and lack of memory for events of patients.
+Its maximum effect usually takes about 2 minutes to take place and it often lasts 5 to 10 minutes.
+
+In our experiment, We set up the dosage to be 200 mg for Biogears and ran it for about 6 mintes. The results are as followed:
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Propofol_HeartRate_vs_Time.jpg}}
+     \caption{Heart Rate changes}
+     \label{fig:given 200 mg Propofol}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Propofol_OxygenSaturation_vs_Time.jpg}}
+     \caption{Oxygen Saturation changes}
+     \label{fig:given 200 mg Propofol}
+   \end{minipage}
+\end{figure}
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Propofol_ArterialPressure_vs_Time.jpg}}
+     \caption{Blood Pressure changes}
+     \label{fig:given 200 mg Propofol}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Propofol_RespirationRate_vs_Time.jpg}}
+     \caption{Respiration Rate changes}
+     \label{fig:given 200 mg Propofol}
+   \end{minipage}
+\end{figure}
 

### 2016-02-24 data-processing-script/plot.py
Draw a plot on physiological data log.

@@ -1,1 +1,74 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import datetime as dt
+import csv
 
+plot = []
+
+#read the file from the csv_from_cae folder
+csv_file = '2016-02-21_2103_PhysiologicalDataLog.csv'
+df = pd.read_csv('csv_from_cae/'+csv_file, header = None)
+i = 0
+
+#time_stamp
+time_stamp = []
+for row in df[2]:
+        time_stamp.append(row)
+
+#HR
+HR = []
+for row in df[3]:
+        HR.append(int(row))
+
+#SBP
+SBP = []
+for row in df[4]:
+        SBP.append(int(row))
+
+#DBP
+DBP = []
+for row in df[5]:
+        DBP.append(int(row))
+
+#RR
+RR = []
+for row in df[6]:
+        RR.append(int(row))
+
+#SpO2
+SpO2 = []
+for row in df[7]:
+        SpO2.append(int(row))
+
+#plot.append(time_stamp)
+plot.append(HR)
+plot.append(SBP)
+plot.append(DBP)
+plot.append(RR)
+plot.append(SpO2)
+
+#time_stamp
+#HR
+#SBP
+#DBP
+#RR
+#SpO2
+#Barry: I changed the time from string to float because if the time is in string,
+#plt.plot(time_stamp, HR) does not work: it says an array of float numbers is needed.
+for i in range(0, len(time_stamp)):
+    tmp = ""
+    for letter in time_stamp[i]:
+        
+        if (letter.isdigit()):
+            tmp += letter
+    time_stamp[i] = tmp
+
+print time_stamp
+plt.plot(time_stamp, HR)
+plt.plot(time_stamp, SBP)
+plt.plot(time_stamp, DBP)
+plt.plot(time_stamp, RR)
+plt.plot(time_stamp, SpO2)
+plt.title("Physiological Data Log")
+plt.xlabel("Time")
+plt.ylabel("Value")

### 2016-02-24 data-processing-script/plot.py
edited the import

@@ -2,7 +2,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import datetime as dt
 import csv
-
+import pandas as pd
 plot = []
 
 #read the file from the csv_from_cae folder

### 2016-02-24 data-processing-script/plot.py
modified plot graph script to plot text

@@ -1,8 +1,8 @@
 import matplotlib.pyplot as plt
 import numpy as np
-import datetime as dt
-import csv
-
+# import datetime as dt
+# import csv
+import pandas as pd
 plot = []
 
 #read the file from the csv_from_cae folder
@@ -61,14 +61,29 @@ for i in range(0, len(time_stamp)):
         
         if (letter.isdigit()):
             tmp += letter
-    time_stamp[i] = tmp
+    time_stamp[i] = int(tmp[-4:])
 
 print time_stamp
-plt.plot(time_stamp, HR)
-plt.plot(time_stamp, SBP)
-plt.plot(time_stamp, DBP)
-plt.plot(time_stamp, RR)
-plt.plot(time_stamp, SpO2)
+
+from matplotlib.pyplot import cm
+
+nums = np.linspace(0,1,5) - 0.01
+color1=cm.rainbow(nums[0]) #purple  HR
+color2=cm.rainbow(nums[1]) #blue    SBP
+color3=cm.rainbow(nums[2]) #green   DBP
+color4=cm.rainbow(nums[3]) #orange  RR
+color5=cm.rainbow(nums[4]) #red     SpO2
+# print color
+
+for i in range(5):
+    plt.plot(time_stamp, plot[i], color=cm.rainbow(nums[i]))
+
 plt.title("Physiological Data Log")
 plt.xlabel("Time")
 plt.ylabel("Value")
+plt.text(850,80,"purple: HR")
+plt.text(850,70,"blue: SBP")
+plt.text(850,60,"green: DBP")
+plt.text(850,50,"orange: RR")
+plt.text(850,40,"red: SpO2")
+plt.show()

### 2016-02-24 biogears-simulations/pre-processing/combine_data.py
+ drawing code

@@ -1,0 +1,21 @@
+import numpy as np
+import glob, os
+fileList=['bradypnea/AnesthesiaMachineStop30Results/AnesthesiaMachineVariedConfigurationResults.txt',
+'bradypnea/AnesthesiaMachineStop120Results/AnesthesiaMachineVariedConfigurationResults.txt']
+
+if __name__ == '__main__':
+    # path = './drugs/Fentanyl500ugResults/FentanylScenarioResults.txt'
+    selected_data = None;
+    selected_column = 15;
+    for path in fileList:
+        data = np.loadtxt(path, delimiter='\t', skiprows=1)
+        selected = [0, 15]
+        if (selected_data == None):
+            selected_data = data[:,[0,15]]
+        else:
+            print selected_data.shape
+            newData =  data[range(0,selected_data.shape[0]),[15]]
+            print newData.shape
+            selected_data = np.concatenate((selected_data, newData[:,None]), axis=1)
+    np.savetxt("./bradypnea/result.csv", selected_data,
+            fmt='%.2f', delimiter=',', header="time,30,120",comments='')

### 2016-02-24 biogears-simulations/pre-processing/extract_column.py

@@ -1,0 +1,10 @@
+import numpy as np
+
+if __name__ == '__main__':
+    # path = './drugs/Fentanyl500ugResults/FentanylScenarioResults.txt'
+    path = './drugs/Succinylcholine5mgResults/SuccinylcholineScenarioResults.txt'
+    data = np.loadtxt(path, delimiter='\t', skiprows=1)
+    selected = [0, 2, 8, 9, 14, 15]
+    selected_data = data[:,selected]
+    np.savetxt("./drugs/SuccinylcholineScenarioResults.csv", selected_data,
+            fmt='%.2f', delimiter=',', header="time,hr,sp,dp,rr,spo2",comments='')

### 2016-02-26 paper_working_on/paper.tex
restructure the tex and add cae jpg

@@
 
+\graphicspath{{cae_simulation_result/}}
 \title{Biogears in Anesthesia Screen Based Simulation}
@@
 In Simulation-Based medical education particularly, whether the models of physiology incidents or responses are accurate or not will directly affect the credibility of the simulation.
-In this paper, we will give insights into the physiology simulation and compare the current physiology engine Biogears.
-We will evaluation its function by comparing with simulation provided by CAE Muse system.
+In this paper, we will give insights into the physiology simulation and compare the current physiology engine Biogears and CAE Muse software.
+We will evaluation Biogears function by comparing with simulation provided by CAE Muse system.
 In the end, we will conclude on the performance of Biogears on key points such as authenticity, stability as well as commenting on its limitations.
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{bleeding_out_HeartRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_HeartRate_vs_Time.jpg}}
      \caption{heart rate changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{bleeding_out_RespirationRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_RespirationRate_vs_Time.jpg}}
      \caption{respiratory rate changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{30_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/30_OxygenSaturation_vs_Time.jpg}}
      \caption{oxygen saturation changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{120_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/120_OxygenSaturation_vs_Time.jpg}}
      \caption{oxygen saturation changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Succinylcholine_HeartRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_HeartRate_vs_Time.jpg}}
      \caption{Heart Rate changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Succinylcholine_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_OxygenSaturation_vs_Time.jpg}}
      \caption{Oxygen Saturation changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Succinylcholine_ArterialPressure_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_ArterialPressure_vs_Time.jpg}}
      \caption{Blood Pressure changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Succinylcholine_RespirationRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_RespirationRate_vs_Time.jpg}}
      \caption{Respiration Rate changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Rocuronium_HeartRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_HeartRate_vs_Time.jpg}}
      \caption{Heart Rate changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Rocuronium_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_OxygenSaturation_vs_Time.jpg}}
      \caption{Oxygen Saturation changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Rocuronium_ArterialPressure_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_ArterialPressure_vs_Time.jpg}}
      \caption{Blood Pressure changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Rocuronium_RespirationRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_RespirationRate_vs_Time.jpg}}
      \caption{Respiration Rate changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Propofol_HeartRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_HeartRate_vs_Time.jpg}}
      \caption{Heart Rate changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Propofol_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_OxygenSaturation_vs_Time.jpg}}
      \caption{Oxygen Saturation changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Propofol_ArterialPressure_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_ArterialPressure_vs_Time.jpg}}
      \caption{Blood Pressure changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{Propofol_RespirationRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_RespirationRate_vs_Time.jpg}}
      \caption{Respiration Rate changes}
@@
    \end{minipage}
+\end{figure}
+
+\begin{figure}[p]
+    \includegraphics[width=1\textwidth]{cae_propofol_200mg.png}
+    \caption{Propofol vital signs}
+    \label{fig:awesome_image}
 \end{figure}

### 2016-02-26 data-processing-script/plot_csv.py

@@ -1,47 +1,117 @@
 import pandas as pd
+from matplotlib.pyplot import cm
+import matplotlib.pyplot as plt
+import numpy as np
 #PatientTime, SCETime, WorldTime, HR, SBP, DBP, RR, SpO2, MAP, CVP, PAS, PAD, PCWP, CO, VT, PAO2, PACO2, PaO2 , PaCO2 , Hb, Hct, pH, TBody, TBlood, ICP, II, PAN2, Alv. ISO., Alv. SEV., Alv. HAL., Alv. ENF., pvO2, pvCO2, C-SPINE X, C-SPINE Y
-# names = ['SCETime', 'WorldTime', 'HR','SBP','DBP','RR','SpO2','MAP','CVP',
-#         'PAS','PAD','PCWP','CO','VT','PAO2','PACO2','PaO2','PaCO2','Hb',
-#         'Hct','pH','TBody','TBlood', 'ICP','II','PAN2','Alv. ISO.','Alv. SEV.'
-#         'Alv. HAL.','Alv. ENF.','pvO2','pvCO2','C-SPINE X', 'C-SPINE Y']
-def recollect_data(csv_file = '2016-02-21_2103_PhysiologicalDataLog.csv'):
+names = ['PatientTime', 'SCETime', 'WorldTime', 'HR', 'SBP', 'DBP', 'RR', 'SpO2',
+         'MAP', 'CVP', 'PAS', 'PAD', 'PCWP', 'CO', 'VT', 'PAO2', 'PACO2', 'PaO2' ,
+         'PaCO2' , 'Hb', 'Hct', 'pH', 'TBody', 'TBlood', 'ICP', 'II', 'PAN2', 'Alv. ISO.',
+         'Alv. SEV.', 'Alv. HAL.', 'Alv. ENF.', 'pvO2', 'pvCO2', 'C-SPINE X', 'C-SPINE Y']
+def convert_column_to_list(df, column):
+        res = []
+        for item in df[column]:
+                res.append(item)
+        return res
+def recollect_data(csv_file = '2016-02-21_2103_PhysiologicalDataLog.csv', folder_name='succinylcholine-77mg'):
         #read the file from the csv_from_cae folder
-        df = pd.read_csv('csv_from_cae/'+csv_file, header = None)
-        i = 0
+
+        path = '/'.join(['csv_from_cae/output',folder_name, csv_file])
+        df = pd.read_csv(path, skiprows=7, header=0, names=names, index_col='PatientTime')
 
         #time_stamp
[…]

### 2016-02-27 paper_working_on/paper.tex
add cae data, modify pictures for biogears simulation and add one paper

@@
 
-\graphicspath{{cae_simulation_result/}}
+\graphicspath{{cae_simulation_result/}{biogears_simulation_result/}}
+
+%\graphicspath{{biogears_simulation_result/30_and_120_stop_breathing}}
+%\graphicspath{{biogears_simulation_result/bleeding_out}}
+%\graphicspath{{biogears_simulation_result/Propofol200mg}}
+%\graphicspath{{biogears_simulation_result/Fentanyl500ug}}
+%\graphicspath{{biogears_simulation_result/Rocuronium50mg}}
+%\graphicspath{{biogears_simulation_result/Morphine40mg}}
+%\graphicspath{{biogears_simulation_result/Succinylcholine5mg}}
+
 \title{Biogears in Anesthesia Screen Based Simulation}
@@
   Xiao Han\\
-  \and Liewei Ke
-  \and Guan Wang
+  \and Guan Wang\\
+  \and Liewei Ke\\
   \and Mclvor William
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_HeartRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{bleeding_out/bleeding_out_HeartRate_vs_Time.jpg}}
      \caption{heart rate changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_RespirationRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{bleeding_out/bleeding_out_RespirationRate_vs_Time.jpg}}
      \caption{respiratory rate changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/30_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{30_and_120_stop_breathing/30_OxygenSaturation_vs_Time.jpg}}
      \caption{oxygen saturation changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/120_OxygenSaturation_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{30_and_120_stop_breathing/120_OxygenSaturation_vs_Time.jpg}}
      \caption{oxygen saturation changes}
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_HeartRate_vs_Time.jpg}}
-     \caption{Heart Rate changes}
-     \label{fig:given 5 mg Succinylcholine}
-
-   \end{minipage}
-   \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_OxygenSaturation_vs_Time.jpg}}
-     \caption{Oxygen Saturation changes}
-     \label{fig:given 5 mg Succinylcholine}
-   \end{minipage}
-\end{figure}
-
-\begin{figure}[!htb]\centering
-   \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_ArterialPressure_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{Succinylcholine5mg/Succinylcholine_ArterialPressure_vs_Time.jpg}}
      \caption{Blood Pressure changes}
@@
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_RespirationRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{Succinylcholine5mg/Succinylcholine_RespirationRate_vs_Time.jpg}}
      \caption{Respiration Rate changes}
@@
 \end{figure}
+
+The problem with those results are that:1. Simulation result of Arterial Pressure
 
@@
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_HeartRate_vs_Time.jpg}}
-     \caption{Heart Rate changes}
+     \frame{\includegraphics[width=5cm]{Rocuronium50mg/Rocuronium_HeartRate_vs_Time.jpg}}
+     \caption{Rocu Heart Rate changes }
      \label{fig:given 50 mg Rocuronium}
@@
    \end{minipage}
-   \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_OxygenSaturation_vs_Time.jpg}}
-     \caption{Oxygen Saturation changes}
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Rocuronium50mg/Rocuronium_ArterialPressure_vs_Time.jpg}}
+     \caption{Rocu Blood Pressure changes}
      \label{fig:given 50 mg Rocuronium}
+
    \end{minipage}
@@
 
-\begin{figure}[!htb]\centering
-   \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_ArterialPressure_vs_Time.jpg}}
-     \caption{Blood Pressure changes}
-     \label{fig:given 50 mg Rocuronium}
-
-   \end{minipage}
-   \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_RespirationRate_vs_Time.jpg}}
-     \caption{Respiration Rate changes}
-     \label{fig:given 50 mg Rocuronium}
-   \end{minipage}
-\end{figure}
+The respiratory rate and oxygen saturation both looks fine when this drug took effect.
+But Rocuronium was not supposed to cause patient's Arterial Pressure to go up, stay for a minute and then plummet to the bottom.
+Instead, we should see its signal functuating around normal level.
+Also, heart rate graph was supposed to look flat and then fell off cause patient's heart is dying with the drug.
 
@@
 \begin{figure}[!htb]\centering
+
+\end{figure}
+
+\begin{figure}[!htb]\centering
    \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_HeartRate_vs_Time.jpg}}
+     \frame{\includegraphics[width=5cm]{Propofol200mg/Propofol_HeartRate_vs_Time.jpg}}
      \caption{Heart Rate changes}
      \label{fig:given 200 mg Propofol}
-
      \end{minipage}
    \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_OxygenSaturation_vs_Time.jpg}}
-     \caption{Oxygen Saturation changes}
+     \frame{\includegraphics[width=5cm]{Propofol200mg/Propofol_RespirationRate_vs_Time.jpg}}
+     \caption{Respiration Rate changes}
      \label{fig:given 200 mg Propofol}
@@
 
-\begin{figure}[!htb]\centering
-   \begin{minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_ArterialPressure_vs_Time.jpg}}
-     \caption{Blood Pressure changes}
-     \label{fig:given 200 mg Propofol}
+Propofol has a fine-looking simulation of Arterial Pressure, but there appeared to be problems with its heart rate and respiratory rate simulation.
+In the heart rate graph at around 30 - 40 seconds, the pumping rate was not supposed to go down as well as rise again.
+In the respiratory rate graph its reading went down and indicated patient stopped breathing after certain point.
+But we expected the patient to start breathing again and recover at some point because we gave normal dosage for Propofol to function as anaesthetic.
 
-   \end{minipage}
-   \begin {minipage}{0.49\textwidth}
-     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_RespirationRate_vs_Time.jpg}}
-     \caption{Respiration Rate changes}
-     \label{fig:given 200 mg Propofol}
-   \end{minipage}
-\end{figure}
+We then ran the same experiment using Muse and visualize the data, the simulation lasts for 
+10 minutes:
 
@@
 
+Morphine is probably the most common drug that's been used to reduce patients' pain.
+However, it is worth paying attention to if large dosage of morphine is injected into patients because that could cause difficulty breathing, nausea and even death of patients.
+So in medical simulation, it is important to simulate its effect accurately for training.
+
+In our experiment, we set up the dosage to be 40 mg for Biogears and ran it for 9 minutes. The results are as followed:
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Morphine40mg/Morphine_HeartRate_vs_Time.jpg}}
+     \caption{Heart Rate changes}
+     \label{fig:given 40 mg Morphine}
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Morphine40mg/Morphine_RespirationRate_vs_Time.jpg}}
+     \caption{Respiration Rate changes}
+     \label{fig:given 40 mg Morphine}
+   \end{minipage}
+\end{figure}
+
+In reality, Injecting a normal person with 40mg morphine is enough to cause him/her heartrate dropping, less breathing which leads to death eventually.
+However, it seems dramatically increasing morphine dosage won't
+be able to cause patient death which will be a problem if it was utilized for medical training.
+
 \subsubsection{Fentanyl 500 ug Simulation}
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_HeartRate_vs_Time.jpg}}
+     \caption{Heart Rate changes}
+     \label{fig:given 500 ug Fentanyl}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_OxygenSaturation_vs_Time.jpg}}
+     \caption{Oxygen Saturation changes}
+     \label{fig:given 500 ug Fentanyl}
+   \end{minipage}
+\end{figure}
+
+\begin{figure}[!htb]\centering
+   \begin{minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_ArterialPressure_vs_Time.jpg}}
+     \caption{Blood Pressure changes}
+     \label{fig:given 500 ug Fentanyl}
+
+   \end{minipage}
+   \begin {minipage}{0.49\textwidth}
+     \frame{\includegraphics[width=5cm]{Fentanyl500ug/Fentany_RespirationRate_vs_Time.jpg}}
+     \caption{Respiration Rate changes}
+     \label{fig:given 500 ug Fentanyl}
+   \end{minipage}
+\end{figure}
 

### 2016-02-27 data-processing-script/plot_csv.py

@@ -63,8 +63,6 @@ def plot_graph(time_stamp, HR, SBP, DBP, RR, SpO2):
         plot.append(RR)
         plot.append(SpO2)
 
-
-
         nums = np.linspace(0,1,5) - 0.01
         time_stamp = convert_to_float(time_stamp)
 
